Including EW and mixed QCD-EW corrections into PDF fits

### 2020-03-30 paper/paper.tex
Cleanup

\section{Introduction}
\label{sec:introduction}

ERN

The impact of EW corrections to LHC data.\\
How to do that consistently, include systematically EW corrections, blabla.\\
Outline a possible strategy to deal with EW correction in LHC observables (FSR, PHOTOS, dressed/born, ...).\\
Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\

\section{Binning phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
\label{sec:pineappl}

\input{pineappl}

\section{Results}
\label{sec:results}

SC

For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
- compute data/prediction plots\\
- compute chi2\\

\section{Double counting}

Count von Count, ALL

Explain the problem to experimentalists.\\

\section{Outlook}

ALL

\cite{Carli:2010rw}
\cite{Bertone:2014zva}

>>>>

\input{sec-introduction}
\input{sec-pineappl}
\input{sec-results}
\input{sec-doublecounting}
\input{sec-conclusion}
